NGO analysis

### 2022-07-22 Shiny/Test/Flexdashboard rows.Rmd
Merging currency caption functions. Commenting.

  output$arsresultat_plotly <- renderPlotly(
    ggplotly(arsresultat_plot()) |>
      ## ggplot subtitles and captions are lost when using ggplotly(), a
      ## currency warning caption is therefore added in plotly, if needed, using
      ## a separate function
      layout(
        annotations =
          plotly_caption()
      )
  )

@@

  output$balance_plotly <- renderPlotly(
    ggplotly(balance_plot()) |>
      ## ggplot subtitles and captions are lost when using ggplotly(), a
      ## currency warning caption is therefore added in plotly, if needed, using
      ## a separate function
      layout(
        annotations =
          plotly_caption()
      )
  )

@@

  output$expenses_plotly <- renderPlotly(
    ggplotly(expenses_plot())
  )

@@

  output$revenue_plotly <- renderPlotly(
    ggplotly(revenue_plot())
  )

@@

  # Reactive function to test for Excel data quality (basic)
  datatest <- reactive({
    if (mean(unlist(lapply(exceldata(), is.character))) != 0) {
      TRUE
    } else {
      FALSE
    }
  })

@@

  # Reactive function to create currency caption
  currency_caption <- reactive({
    # Checking for uniform currency code
    if (length(unique(htmldata()$valutakode)) == 1) {
      # Empty caption if uniform
      ""
      # Warning if multiple currencies
    } else {
      "Note: not all values are denominated in the same currency"
    }
  })

  # Reactive function to create plotly caption
  # (ggplot captions and subtitles are lost in the conversion)
  # (shamelessly stolen from the Internet, with minor modifications)
  plotly_caption <- reactive({
    list(
      x = 1, y = -0.1, text = currency_caption(),
      showarrow = F, xref = "paper", yref = "paper",
      xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
      font = list(size = 11)
    )
  })

@@

```{r non-reactive functions, include=FALSE}
# Function to read html file
read_proff <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    select( # removing empty column
      REGNSKAPSPERIODE:all_of(start)
    ) |> # using all_of()
    mutate( # removing whitespace
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    filter( # removing duplicate table - no idea why it's necessary
      !row_number() > 176
    ) |>
    filter( # removing duplicate rows
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    pivot_longer( # tidying data
      all_of(end):all_of(start),
      names_to = "year"
    ) |> # using all_of()
    mutate( # changing to real NAs and turning years into numbers
      value = na_if(value, "-"),
      year = as.integer(year),
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |>
    fill( # filling the currency column
      valutakode,
      .direction = "updown"
    ) |>
    filter( # removing dates and redundant currency
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate( # removing whitespace in numbers
      value = str_replace_all(value, "\\s", ""),
      value = as.numeric(value),
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    ) |>
    distinct() |> # removing any remaining duplicate rows
    pivot_wider( # pivoting
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    clean_names() |> # tidying names
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |> # removing headings
    rename( # making it clear what lonn refers to
      lederlonn = lonn
    ) |>
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |>
    arrange(desc(year)) # arranging by year
}

# Test version of function that creates multiple data problems
# read_proff <- function(file, start, end) {
#   read_html(file, encoding = "UTF-8") |>
#     html_node("#inner-frame") |>
#     html_table() |>
#     select( # removing empty column
#       REGNSKAPSPERIODE:all_of(start)
#     ) |> # using all_of()
#     mutate( # removing whitespace
#       REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
#     ) |>
#     filter( # removing duplicate table - no idea why it's necessary
#       !row_number() > 176
#     ) |>
#     filter( # removing duplicate rows
#       !grepl("Lukk", REGNSKAPSPERIODE)
#     ) |>
#     pivot_longer( # tidying data
#       all_of(end):all_of(start),
#       names_to = "year"
#     ) |> # using all_of()
#     mutate( # changing to real NAs and turning years into numbers
#       value = na_if(value, "-"),
#       year = as.integer(year),
#       valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
#     ) |>
#     fill( # filling the currency column
#       valutakode,
#       .direction = "updown"
#     ) |>
#     filter( # removing dates and redundant currency
#       REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
#         REGNSKAPSPERIODE != "Valutakode"
#     ) |>
#     mutate( # removing whitespace in numbers
#       value = str_replace_all(value, "\\s", ""),
#       value = as.numeric(value),
#       value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
#     ) |>
#     distinct() |> # removing any remaining duplicate rows
#     pivot_wider( # pivoting
#       names_from = REGNSKAPSPERIODE, values_from = value
#     ) |>
#     clean_names() |> # tidying names
#     select(
#       -lederlonn_i_hele_1000,
#       -resultatregnskap_i_hele_1000,
#       -balanseregnskap_i_hele_1000
#     ) |> # removing headings
#     rename( # making it clear what lonn refers to
#       lederlonn = lonn
#     ) |>
#     # Creating new variables for plots
#     mutate(
#       annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
#       balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
#     ) |>
#     # bad test - REMOVE
#     mutate(
#       valutakode = ifelse(year == 2019, "USD", valutakode),
#       leder_annen_godtgjorelse = NA,
#       lederlonn = NA,
#       arsresultat = NA,
#       sum_egenkapital_og_gjeld = NA
#     ) |>
#     arrange(desc(year)) # arranging by year
# }

>>>>

  # Creating plotly output
  output$arsresultat_plotly <- renderPlotly(
    ggplotly(arsresultat_plot()) |>
      ## ggplot subtitles and captions are lost when using ggplotly(), a
      ## currency warning caption is therefore added in plotly, if needed, using
      ## a separate function
      layout(
        annotations =
          plotly_caption()
      )
  )

@@

  # Creating plotly output
  output$balance_plotly <- renderPlotly(
    ggplotly(balance_plot()) |>
      ## ggplot subtitles and captions are lost when using ggplotly(), a
      ## currency warning caption is therefore added in plotly, if needed, using
      ## a separate function
      layout(
        annotations =
          plotly_caption()
      )
  )

@@

  # Creating plotly output
  output$expenses_plotly <- renderPlotly(
    ggplotly(expenses_plot())
  )

@@

  # Creating plotly output
  output$revenue_plotly <- renderPlotly(
    ggplotly(revenue_plot())
  )

@@

  # Reactive function to test for Excel data quality (basic)
  datatest <- reactive({
    # let me know if anyone has a better idea for testing
    if (mean(unlist(lapply(exceldata(), is.character))) != 0) {
      TRUE
    } else {
      FALSE
    }
  })

@@

  # Reactive function to create plotly caption (ggplot captions and subtitles
  # are lost in the conversion) (shamelessly stolen from the Internet, with
  # minor modifications).
  # Checks for uniform currency code and prints a warning
  # if there are multiple currency codes.
  plotly_caption <- reactive({
    list(
      x = 1, y = -0.1, text = ifelse(length(unique(htmldata()$valutakode)) == 1,
        "", "Note: not all values are denominated in the same currency"
      ),
      showarrow = F, xref = "paper", yref = "paper",
      xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
      font = list(size = 11)
    )
  })

@@

```{r non-reactive functions, include=FALSE}
# Function to read html file
# read_proff <- function(file, start, end) {
#   read_html(file, encoding = "UTF-8") |>
#     html_node("#inner-frame") |>
#     html_table() |>
#     select( # removing empty column
#       REGNSKAPSPERIODE:all_of(start)
#     ) |> # using all_of()
#     mutate( # removing whitespace
#       REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
#     ) |>
#     filter( # removing duplicate table - no idea why it's necessary
#       !row_number() > 176
#     ) |>
#     filter( # removing duplicate rows
#       !grepl("Lukk", REGNSKAPSPERIODE)
#     ) |>
#     pivot_longer( # tidying data
#       all_of(end):all_of(start),
#       names_to = "year"
#     ) |> # using all_of()
#     mutate( # changing to real NAs and turning years into numbers
#       value = na_if(value, "-"),
#       year = as.integer(year),
#       valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
#     ) |>
#     fill( # filling the currency column
#       valutakode,
#       .direction = "updown"
#     ) |>
#     filter( # removing dates and redundant currency
#       REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
#         REGNSKAPSPERIODE != "Valutakode"
#     ) |>
#     mutate( # removing whitespace in numbers
#       value = str_replace_all(value, "\\s", ""),
#       value = as.numeric(value),
#       value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
#     ) |>
#     distinct() |> # removing any remaining duplicate rows
#     pivot_wider( # pivoting
#       names_from = REGNSKAPSPERIODE, values_from = value
#     ) |>
#     clean_names() |> # tidying names
#     select(
#       -lederlonn_i_hele_1000,
#       -resultatregnskap_i_hele_1000,
#       -balanseregnskap_i_hele_1000
#     ) |> # removing headings
#     rename( # making it clear what lonn refers to
#       lederlonn = lonn
#     ) |>
#     # Creating new variables for plots
#     mutate(
#       annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
#       balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
#     ) |>
#     arrange(desc(year)) # arranging by year
# }

# Test version of function that creates multiple data problems
read_proff <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    select( # removing empty column
      REGNSKAPSPERIODE:all_of(start)
    ) |> # using all_of()
    mutate( # removing whitespace
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    filter( # removing duplicate table - no idea why it's necessary
      !row_number() > 176
    ) |>
    filter( # removing duplicate rows
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    pivot_longer( # tidying data
      all_of(end):all_of(start),
      names_to = "year"
    ) |> # using all_of()
    mutate( # changing to real NAs and turning years into numbers
      value = na_if(value, "-"),
      year = as.integer(year),
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |>
    fill( # filling the currency column
      valutakode,
      .direction = "updown"
    ) |>
    filter( # removing dates and redundant currency
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate( # removing whitespace in numbers
      value = str_replace_all(value, "\\s", ""),
      value = as.numeric(value),
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    ) |>
    distinct() |> # removing any remaining duplicate rows
    pivot_wider( # pivoting
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    clean_names() |> # tidying names
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |> # removing headings
    rename( # making it clear what lonn refers to
      lederlonn = lonn
    ) |>
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |>
    # bad test - REMOVE
    mutate(
      valutakode = ifelse(year == 2019, "USD", valutakode)
    ) |>
    arrange(desc(year)) # arranging by year
}

# ,
#       leder_annen_godtgjorelse = NA,
#       lederlonn = NA,
#       arsresultat = NA,
#       sum_egenkapital_og_gjeld = NA
